State of the Art in \\ {\ttlit Twitter Sentiment Analysis}

### 2015-01-22 paper/chapters/4_classification.tex
Paper: features

\subsection{Features}
As twitter messages are composed of an arbitrary number of words makes it necessary to extract exactly those words which preferably describes the characteristics of such tweets. Extracting those words to an object by making use of various word selecting techniques is called a feature vector. These word selecting techniques are a fundamental process for providing informations to the classification methods, thus an extensive body of different word selecting algorithms exist. 
	\emph{Term Presence} is a method where the feature vector consists of a binary value, $0$ for "term is not present" and $1$ for "term is present". A similar approach is to count the number of occurred words in a message and use the numeric value as a feature, which is called \emph{Term Frequency} but Pang et al. showed \autocite{Pang2008} that Term Presence performed better compared to Term Frequency.
TODO

>>>>

\subsection{Features}
Since twitter messages are composed of an arbitrary number of words, classification makes it necessary to extract exactly those words which preferably describes the characteristics of such tweets. The extraction of those words by the use of various word selecting techniques is called a  feature vector. These word selecting techniques are a fundamental process for providing informations to the classification methods, thus an extensive body of different word selecting algorithms exist. An overview is provided by Pang et al. \autocite{Pang2008} which can be summarized as follows:\\
\emph{Term Presence} is a word selecting technique where the feature vector consists of a binary value, $0$ for "term is not present" and $1$ for "term is present".\\
A similar approach is to count the number of occurred words in a message and make use of the numeric value as a feature, which is called \emph{Term Frequency}.\\
\emph{Term-based Features Beyond Term Unigrams} describes the encoding of position informations within a textual unit (e.g., at the end of the document)  into the feature vectors. This technique is based on the idea that the position of textual units can have influence on the importance of these.\\
The idea of \emph{Part-of-Speech} (POS) informations is to make use of labeled words within the tweet by diversifying them into categories of words. As soon as the words are labeled, they can be filtered (f.e. by adjectives and verbs only which can be a strong indicator for sentiment) and the result can be applied to the feature vectors.\\
